RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-27 system.tex
yes

Implicit signaling of interest is supported by keeping click-through
\cite{Joachims:2005:AIC} and execution counts. (In addition to these
classic web search techniques of collecting feedback, we have the
prospect of applying static and dynamic code analysis to generate
further fine-grained information about relationships, for example,
which packages and data sets often appear together.)

\todo{explain} These will be ingredients for the recommendation system.

@@

A key engineering decision in RCloud was to rely on full two-way
communication between human interface in a web client, and remote
data and computing resources in the cloud.

>>>>

Implicit signaling of interest is supported by keeping click-through
\cite{Joachims:2005:AIC} and execution counts. (In addition to these
classic techniques of collecting feedback from web search, we anticipate
applying static and dynamic code analysis to generate fine-grained
information about relationships, for example, which packages and data
sets often appear together.)

@@

A key engineering decision in RCloud was to rely on full two-way
communication between the web client human interface, and data and
computing resources in the cloud. It is easier to engineer a design
in which the human interface is pushed one-way from the server
and thereafter all interaction takes place within the client.
Two-way communication is necessary, though, where the size of
the data or computational performance makes it impractical to
move all computation to the client.
